### 2013-04-01 exam6/2.tex
Tweak to thunk problem.
more tweaks.
Java interface reference.

@@

A \emph{binary search tree} is a lot like a binary tree in that a BST
is either a node, which contains an element and a left and right
subtree, or a leaf, which doesn't contain an element or subtrees.  The
difference between a binary tree and a binary \emph{search} tree is
that every leaf and node of a BST also contains a \texttt{Comparator},
and nodes have the following invariant: every element in the left
subtree is smaller (according to the comparator) than the element in
the node, which in turn is smaller than or equal (according to the
comparator) to every element in the right subtree.  (You can assume
the comparator in every leaf and node is the same for any given BST.)

@@

\newpage
\item Here's an idea for sorting a series of elements: take all of the
 elements and insert them into (an initially empty) binary search
 tree.  Now, assuming \texttt{BST<X>} implemented the
 \texttt{Iterable<X>} such that the iterator produced by
 \texttt{iterator()} visited the elements of the BST in increasing
 order (according to the comparator), then the elements could be retrieved
in sorted order.

Use this idea to implement a sorting method with the signature given
 below.  It should sort a given iterable object in ascending order
 according to a given comparator, producing the sorted list as an
 array list of elements.

You may assume \texttt{BST<X>} implements \texttt{Iterable<X>} correctly
and do not need to define this yourself (see the extra credit).

@@

\begin{problem} \pts{25}
\noindent
Tobin-Hochstadt has been asked to serve on a review panel for the
National Science Foundation, which requires he read and make notes on
a set of grant proposals the government is considering to fund.
Rather than read the proposals, he's decided to make a program for
modeling his notes.  His notes take the form of an outline, which
consists of a peice of text and a list of (sub)notes.  For example,
here's one of his notes (thankfully not in his handwritting):
\begin{verbatim}
       NSF Proposal 1218390
       |
       +- Overview
       |  |
       |  +- WAT?
       |  |
       |  +- Motivations
       |     |
       |     +- unmotivating
       |
       +- Middle (fell asleep)
       |
       +- Conclusions
       |
       +- Budget
          |
          +- very large
          |
          +- underfund lots of BU undergrads
\end{verbatim}

@@

\begin{verbatim}
Boolean sameNote(Note s) { ...}

@@

  // If this computation has never been run, run
  // compute and produce its result.  Remember
  // this answer for future runs and just return
  // it rather than re-run compute.
  R run();
}
\end{verbatim}
\end{enumerate}

@@

// Never run, so never blows up.
new MaybeOnce<Integer>(new BlowUp())
\end{verbatim}

@@

\noindent
Revise your design of \texttt{BST<X>} to implement
 \texttt{Iterable<X>} interface.  The iterator returned by
 \texttt{iterator()} should iterate through the elements in sorted order.

>>>>

\begin{center}
{\bf Java Reference}
\end{center}
\noindent
You may be asked to use or implement the following standard Java
interfaces, which are described here for reference:

\begin{enumerate}
\item \texttt{Iterable<X>} -- Implementing this interface allows an object to be the target of the ``foreach'' statement.

 Methods:
 \begin{itemize}
 \item \texttt{Iterator<X> iterator()} : Returns an iterator over a set of
  elements of type \texttt{X}.
  \end{itemize}

\item \texttt{Iterator<X>} -- An iterator over a collection.

  Methods:
  \begin{itemize}
    \item \texttt{boolean hasNext()} : Returns \texttt{true} if the iteration
      has more elements.
    \item \texttt{X next()} : Returns the next element in the iteration.
  \end{itemize}

\item \texttt{Comparator<X>} -- A comparison function, which imposes a total ordering on some collection of objects.

  Methods:
  \begin{itemize}
    \item \texttt{int compare(X o1, X o2)} : Compares its two
      arguments for order. Returns a negative integer, zero, or a
      positive integer as the first argument is less than, equal to,
      or greater than the second.
  \end{itemize}

\end{enumerate}

@@

A \emph{binary search tree} (BST) is a lot like a binary tree in that
a BST is either a node, which contains an element and a left and right
subtree, or a leaf, which contains neither elements nor subtrees.  The
difference between a binary tree and a binary \emph{search} tree is
that every leaf and node of a BST also contains a \texttt{Comparator},
and nodes have the following invariant: every element in the left
subtree is smaller (according to the comparator) than the element in
the node, which in turn is smaller than or equal to (according to the
comparator) every element in the right subtree.  (You can assume
the comparator in every leaf and node is the same for any given BST.)

@@

\newpage
\item Here's an idea for sorting a series of elements: take all of the
 elements and insert them into (an initially empty) binary search
 tree.  Now, assuming \texttt{BST<X>} implemented the
 \texttt{Iterable<X>} interface such that the iterator produced by
 \texttt{iterator()} visited the elements of the BST in increasing
 order (according to the comparator), then the elements could be retrieved
in sorted order.

Use this idea to implement a sorting method with the signature given
 below.  It should sort the elements of a given iterable object in ascending order
 according to a given comparator, producing the sorted elements as an
 array list.

You may assume \texttt{BST<X>} implements \texttt{Iterable<X>} correctly
and do not need to define this yourself (see the extra credit problem).

@@

\begin{problem} \pts{25}
\noindent
Tobin-Hochstadt has been asked to serve on a review panel for the
 National Science Foundation, which requires he read and make notes on
 a set of grant proposals the government is considering to fund.
  Rather than read the proposals he's been assigned, he's decided to
 make a program for modeling his notes.  His notes take the form of an
 outline, which consists of a peice of text and a list of (sub)notes.
  For example, here's one of his notes (thankfully not in his
 handwritting):
\begin{verbatim}
       NSF Proposal 1218390
       |
       +- Overview
       |  |
       |  +- WAT?
       |  |
       |  +- Motivations
       |     |
       |     +- unmotivating
       |
       +- Middle (fell asleep)
       |
       +- Conclusions
       |
       +- Budget
          |
          +- very large
          |
          +- underfund lots of BU undergrads
\end{verbatim}

@@

\begin{verbatim}
Boolean sameNote(Note s) { ... }

@@

  // If this computation has never been run, run
  // compute and produce its result.  Remember
  // this answer for future runs and just return
  // it rather than re-run compute.
  R run() { ... }
}
\end{verbatim}

@@

// Never run, so never blows up.
new MaybeOnce<Integer>(new BlowUp())
\end{verbatim}
\end{enumerate}

@@

\noindent
Revise your design of \texttt{BST<X>} to implement
 \texttt{Iterable<X>} interface.  The iterator returned by
 \texttt{iterator()} should iterate through the elements in sorted order.
 It should do this efficiently by relying on the \texttt{BST} invariant.
